Designing Types for R, Empirically

### 2020-10-09 paper/main.tex
prelim discussion of different consolidation options, as itemize

>>>>

%
%
%
%
\section{Discussion}

\AT{Let's discuss alternative strategies for consolidating types here.}

\begin{itemize}
	\item We employed the following strategy to consolidate types: We collected all of the traces observed for a function, and combined them into a single function type, where the type for each argument position was made up of a union of all of the observed types at that position.
	\item We then simplified these unions using the rules \AT{discussed previously, ref section.}
	\item We did not develop this strategy in a vacuum, and there are indeed alternatives worth mentioning.

	\item For starters, one may rightly argue that our strategy results in a loss of precision, as relationships between input and output types are obscured.
	\item For example, consider a function with two unique call traces, \FUN{\chr}{\chr} and \FUN{\dbl}{\dbl}.
	\item The strategy we employed results in a combined type of \FUN{\chr \;|\; \dbl}{\chr \;|\; \dbl} for the function, which obscures the (potential) relationship between the argument and return type.

	\item An obvious solution to this is simply to convert each call trace into a type, and generate a union of function types as the overall type for the function.
	\item This would lead to the type  \FUN{\chr}{\chr} $|$ \FUN{\dbl}{\dbl} for the aforementioned function.
	\item Unfortunately, this leads to a significant blow-up in the size of types, and makes many types unreadable, due to the myriad ways in which we combine the primitive types, as recall that, e.g., scalars and vectors are not the same type, and we see many types of the form \FUN{\chr}{\dbl} $|$ \FUN{\VEC\chr}{\dbl} $|$ \FUN{\NAVEC\chr}{\dbl}.
	\item To quickly compare this consolidation strategy against the one employed throughout the paper, we find that the types \AT{put numbers, gist is that it's bigger and more incomprehensible.}

	\item Another option is to employ a hybrid approach, wherein we perform a union of function types {\it after} grouping them together by return type, and performing basic primitive type consolidation on the return types.
	\item This has the advantage of avoiding most of the blowup of the naive approach, however this hybrid  approach suffers particularly when functions return classes, as effectively consolidating class types is unclear given the limited level of detail in our type system.
	\item Comparing again to the strategy employed throughout the paper, we see \AT{numbers, it's a bit bigger, not too much. Need numbers of unions, etc. Forthcoming.}

	\item \AT{Will pull in example showcasing the different strategies.}
\end{itemize}
